Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2023-09-14 manuscript.qmd
Added code for auto-downloading of data files

processdata <- 0

@@

# create python environment and install packages
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}

use_virtualenv('env/')

@@

mnechans <- read.csv('local/MNEchannels.csv')
mnechans <- mnechans[c(1:12,14:18,20:64),1]  # exclude the mastoids

chandata <- read.csv('local/channeldata.csv')

electrodeindices <- match(toupper(mnechans),chandata$Electrode)

figdir <- 'Figures/'

@@

  for subj in range(0,len(sublist)):
    filename = "local/preprocessed/S" + str(sublist[subj]) + ".set"
    raw = mne.io.read_raw_eeglab(filename,preload=True)
    raw.drop_channels(["HEOG", "VEOG", "M1", "M2"])
    raw.set_montage(ANT_montage)

@@

  for subj in range(0,len(sublist)):
    filename = "local/preprocessed/S" + str(sublist[subj]) + ".set"

>>>>

processdata <- 0
# the processdata flag has three levels:
# 0 - just produce the manuscript with minimal analysis, using existing figures
# 1 - do group-level analysis using pre-computed MVPA and ERPs (requires 200MB)
# 2 - do all analyses from scratch using the raw data (requires ~35GB)

@@

# create python environment and install packages
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}
use_virtualenv('env/')

@@

# check for local files and directories and create/download if missing
if (!dir.exists('local')){dir.create('local')}
figdir <- 'Figures/'
if (!dir.exists(figdir)){dir.create(figdir)}

if (processdata>0){
if (!file.exists('local/MNEchannels.csv')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('MNEchannels.csv',osffiles$name)
osf_download(osffiles[fid,],path='local/')
}
if (!file.exists('local/channeldata.csv')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('channeldata.csv',osffiles$name)
osf_download(osffiles[fid,],path='local/')
}

chandata <- read.csv('local/channeldata.csv')
mnechans <- read.csv('local/MNEchannels.csv')
mnechans <- mnechans[c(1:12,14:18,20:64),1]  # exclude the mastoids
electrodeindices <- match(toupper(mnechans),chandata$Electrode)
}

if (processdata<2){
  # download processed data if missing
  if (!file.exists('local/Expt1resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt1resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Expt2resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt2resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Exp1Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp1Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
}

if (processdata==2){
  # check for presence of raw data and download if missing
  if (!dir.exists('local/rawdata')){dir.create('local/rawdata')}
  d <- dir('local/rawdata/',pattern='S')
  if (length(d)<126){
    osfproject <- osf_retrieve_node("yhsmb")
    osffiles <- osf_ls_files(osfproject,n_max=300)
    for (n in 1:nrow(osffiles)){
      if (!pmatch(osffiles[n,]$name,d,nomatch=0)){
        osf_download(osffiles[n,],path='local/rawdata/',progress=TRUE)
      }
    }
    osfproject <- osf_retrieve_node("dhkcg")
    osffiles <- osf_ls_files(osfproject,n_max=300)
    for (n in 1:nrow(osffiles)){
      if (!pmatch(osffiles[n,]$name,d,nomatch=0)){
        osf_download(osffiles[n,],path='local/rawdata/',progress=TRUE)
      }
    }    
  }
}

@@

  for subj in range(0,len(sublist)):
    filename = "local/rawdata/S" + str(sublist[subj]) + ".set"
    raw = mne.io.read_raw_eeglab(filename,preload=True)
    raw.drop_channels(["HEOG", "VEOG", "M1", "M2"])
    raw.set_montage(ANT_montage)

@@

  for subj in range(0,len(sublist)):
    filename = "local/rawdata/S" + str(sublist[subj]) + ".set"
